---
title: "Introduction to keystats"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro_Keystats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Anna Sophie Peters, Nurah Jaradat, Jiner Zheng 
### 12 December 2019

This function allows Twitter users to search the website by keyword or hashtag,
returning multiple graphics and statistical summaries such as a bar plot of 
related unique words, a word cloud, a radar chart, and two bar plots of location 
statistics.

-----

### Usage of the function:

```{r, include = TRUE, eval=FALSE}
keystats(key, n = 10000, top_num = 10, graph_col = "dodgerblue3")

```

-----

### Arguments of the function:

key: The keyword or hashtag that the user of this function wishes to analyze

n: The number of tweets relating to key that the user of this function wishes to analyze. The maximum number of tweets to analyze at once is 18,000. Default = 10,000

top_num: The number of top words/hashtags/locations displayed in the HTML output. Default = 10

graph_col: The color of graphs in the HTML output. Default = "dodgerblue3"

-----

### Example:

```{r, include = TRUE, eval=FALSE}
library(rtweetstats)
keystats("data science", n=1000, top_num = 20)
```
