---
title: "Introduction to userstats"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro_Userstats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Anna Sophie Peters, Nurah Jaradat, Jiner Zheng 
### 12 December 2019

This function allows Twitter users to search the website by username, allowing 
the user to search multiple usernames at one time, specify which year they would 
like summary information for, specify the number of tweets they would like to 
analyze (with a maximum output allowed of 3,200 tweets), customize the background 
color of output tables, and customize the text color of the output with the 
assumption of knowledge of HTML color codes.

-----

### Usage of the function:

```{r, include = TRUE, eval=FALSE}
userstats(user, n = 1000, bg_col = "white", txt_col = "#1A5276", year = 2019, x = 10)
```

-----

### Arguments of the function:

user: The username of a real Twitter account that the user of this function wishes to analyze

n: The number of tweets the user of this function wishes to analyze from the desired account. Default = 1000

bg_col: The background color of all tables in the HTML output. Default = "white"

txt_col: The text color of all tables in the HTML output. Default = "#1A5276"

year: The year during which the tweets the user wishes to analyze were published. Default = 2019

x: The number of recent tweets the user wishes to display from the indicated account in the HTML output. Default = 10

-----

### Example:

```{r, include = TRUE, eval=FALSE}
library(rtweetstats)
userstats(c("taylorswift13","21savage","trvisxx","katyperry"), 1000, year=2019, x = 3)
```
